\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-10-25 doc/USER_MANUAL/01_introduction.tex
better BibTeX

@@

If you use the C-PML absorbing layer capabilities of the code, please cite at least one article
written by the developers of the package, for instance:
%
\begin{itemize}
\item \cite{XiKoMaMa14},
\item \cite{XiMaCrKoMa16}.
\end{itemize}
%
If you use the attenuation (anelastic/viscoelastic) capabilities of the code, please cite at least one article
written by the developers of the package, for instance:
%
\begin{itemize}
\item \cite{BlKoChLoXi16}.
\end{itemize}
%
If you use the kernel capabilities of the code, please cite at least one article
written by the developers of the package, for instance:
%
\begin{itemize}
\item \cite{TrKoLi08},
\item \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11},
\item \cite{LiTr06},
\item \cite{MoLuTr09}.
\end{itemize}

>>>>

You can find all the references below in \BibTeX format in file \texttt{doc/USER\_MANUAL/bibliography.bib}.\\

@@

If you use the C-PML absorbing layer capabilities of the code, please cite at least one article
written by the developers of the package, for instance:
%
\begin{itemize}
\item \cite{XiKoMaMa14},
\item \cite{XiMaCrKoMa16}.
\end{itemize}
%
If you use the UNDO\_ATTENUATION option of the code in order to produce full anelastic/viscoelastic sensitivity kernels, please cite at least one article
written by the developers of the package, for instance (and in particular):
%
\begin{itemize}
\item \cite{KoXiBoPeSaLiTr16}.
\end{itemize}
%
More generally, if you use the attenuation (anelastic/viscoelastic) capabilities of the code, please cite at least one article
written by the developers of the package, for instance:
%
\begin{itemize}
\item \cite{KoXiBoPeSaLiTr16},
\item \cite{BlKoChLoXi16}.
\end{itemize}
%
If you use the kernel capabilities of the code, please cite at least one article
written by the developers of the package, for instance:
%
\begin{itemize}
\item \cite{TrKoLi08},
\item \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11},
\item \cite{LiTr06},
\item \cite{MoLuTr09}.
\end{itemize}

### 2016-10-25 doc/USER_MANUAL/03_mesh_generation.tex

Please note that your Vp- and Vs-speeds are given for a reference frequency. To change
this reference frequency, you change the value of \texttt{ATTENUATION\_f0\_REFERENCE}
in the main constants file \texttt{constants.h} found in subdirectory
\texttt{src/shared/}.
\item [{anisotropic\_flag}] Flag describing the anisotropic model to use
in case an anisotropic simulation should be conducted. See the file
\texttt{model\_aniso.f90} in subdirectory \texttt{src/generate\_databases/}
for an implementation of the anisotropic models. In case no anisotropy
is available, it can be set to zero.
\end{description}

@@

where \texttt{\textbf{domain\_ID}}\textbf{ is 1 for acoustic and 2
for elastic or viscoelastic materials,} \texttt{material\_ID} a unique
identifier, \texttt{rho} the density in $kg\, m^{-3}$, \texttt{vp}
the P-wave speed in $m\, s^{-1}$, \texttt{vs} the S-wave speed in
$m\, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag}
an identifier for anisotropic models. Note that the \texttt{Qkappa}
value is ignored by the code unless \texttt{FULL\_ATTENUATION\_SOLID}
is set. Note also that both \texttt{Qkappa} and \texttt{Qmu} are ignored
by the code unless \texttt{ATTENUATION} is set. If you want a model
with no \texttt{Qmu} attenuation, both set \texttt{ATTENUATION} to
\texttt{.false.} in the \texttt{Par\_file} and set \texttt{Qmu} to
9999 here. If you want a model with no \texttt{Qkappa} attenuation,
both set \texttt{FULL\_ATTENUATION\_SOLID} to \texttt{.false.} in
the \texttt{Par\_file} and set \texttt{Qkappa} to 9999 here.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp. To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

>>>>

Please note that your Vp- and Vs-speeds are given for a reference frequency. To change
this reference frequency, you change the value of \texttt{ATTENUATION\_f0\_REFERENCE}
in the main constants file \texttt{constants.h} found in subdirectory
\texttt{src/shared/}.
The code uses a constant $Q$ quality factor, write(IMAIN,*) "but approximated based on a series of Zener standard linear solids (SLS).
The approximation is thus performed in a given frequency band determined based on that \texttt{ATTENUATION\_f0\_REFERENCE} reference frequency.
\item [{anisotropic\_flag}] Flag describing the anisotropic model to use
in case an anisotropic simulation should be conducted. See the file
\texttt{model\_aniso.f90} in subdirectory \texttt{src/generate\_databases/}
for an implementation of the anisotropic models. In case no anisotropy
is available, it can be set to zero.
\end{description}

@@

where \texttt{\textbf{domain\_ID}}\textbf{ is 1 for acoustic and 2
for elastic or viscoelastic materials,} \texttt{material\_ID} a unique
identifier, \texttt{rho} the density in $kg\, m^{-3}$, \texttt{vp}
the P-wave speed in $m\, s^{-1}$, \texttt{vs} the S-wave speed in
$m\, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag}
an identifier for anisotropic models.
Note that both \texttt{Qkappa} and \texttt{Qmu} are ignored
by the code unless \texttt{ATTENUATION} is set. If you want a model
with no \texttt{Qmu} attenuation, both set \texttt{ATTENUATION} to
\texttt{.false.} in the \texttt{Par\_file} and set \texttt{Qmu} to
9999 here. If you want a model with no \texttt{Qkappa} attenuation, set \texttt{Qkappa} to 9999 here.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp. To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

### 2016-10-25 doc/USER_MANUAL/06_fault_sources.tex
Modified contents in user manual chapter 6.
Buildbot ran the code beautifier.

To facilitate the mesh generation with split nodes in CUBIT, we need
to separate the two fault surfaces by a small distance, effectively
creating a tiny opening of the fault (Figure \ref{fig:examples.splitnodes},
\ref{fig:examples.splitnodes-surfacetrace}). Note that only the interior
of the fault must be opened, its edges must remain closed (except
the edge on the free surface). The fault is automatically closed later
by SPECFEM3D.\\

@@

\&\textbf{DIST2D} shape='$\mathtt{square}$', val, xc, yc, zc, l /

@@

\&\textbf{DIST2D} shape='$\mathtt{rectangle}$', val, xc, yc, zc,
lx, ly, lz /

@@

\&\textbf{DIST2D} shape='$\mathtt{rectangle-taper}$', val, valh,
xc, yc, zc, lx, ly, lz /

@@

\&\textbf{DIST2D} shape='$\mathtt{circular}$', val, xc, yc, zc, r
/

>>>>

To facilitate the mesh generation with split nodes in CUBIT, we need
to separate the two fault surfaces by a small distance, effectively
creating a tiny opening of the fault (Figure \ref{fig:examples.splitnodes},
\ref{fig:examples.splitnodes-surfacetrace}). Note that the opening distance
should not be too small especially in single precision simulations
(For example, if your fault is at $y=y_0$ plane, then the opening distance
should be at least $10^{-6}y_0$ since single precision can ensure precision
within only 7 digits). Note that only the interior
of the fault must be opened, its edges must remain closed (except
the edge on the free surface). The fault is automatically closed later
by SPECFEM3D.\\

@@

\&\textbf{DIST2D} shapeval='$\mathtt{square}$', val, xc, yc, zc, l /

@@

\&\textbf{DIST2D} shapeval='$\mathtt{rectangle}$', val, xc, yc, zc,
lx, ly, lz /

@@

\&\textbf{DIST2D} shapeval='$\mathtt{rectangle-taper}$', val, valh,
xc, yc, zc, lx, ly, lz /

@@

\&\textbf{DIST2D} shapeval='$\mathtt{circular}$', val, xc, yc, zc, r
/
